Geometric Control for Autonomous Landing on Asteroids

### 2017-08-09 manuscript.tex
Add some todos for the simulation part
Use local bib file
Add some of the ground truth plots
Update plots
Add some more images and some discussino of the localization

The desired attitude command is chosen such that the spacecraft camera axis, \( \vb{b}_1 \), is directed along the nadir towards the asteroid.
It is sufficient to define two orthogonal vectors to uniquely determine the attitude of the spacecraft.
The \( \vb{b}_{3d} \) vector is chosen to lie in the plane spanned by \(\vb{b}_{1d} \) and \( \vb{e}_3 = \vb{f}_3 \).
The desired attitude command is defined as
\begin{align}
    \vb{b}_{1d} &= - \frac{\vb{x}}{\norm{\vb{x}}} , \\
    \vb{b}_{3d} &= \frac{\vb{f}_3 - \parenth{\vb{f}_3 \cdot \vb{b}_{1d}} \vb{b}_{1d}}{\norm{\vb{f}_3 - \parenth{\vb{f}_3 \cdot \vb{b}_{1d}} \vb{b}_{1d}}}, \\
    \vb{b}_{2d} &= \vb{b}_{3d} \times \vb{1d} , \\
R_d &= \begin{bmatrix} \vb{b}_{1d} & \vb{b}_{2d} & \vb{b}_{3d} \end{bmatrix} .
\end{align}

\section{Conclusions}\label{sec:conclusions}
There have been a variety of approaches for the analysis and design of orbital trajectories around asteroids.
Relatively less work has been directed towards the design of landing trajectories.
Furthermore, much of the previous work has only treated the orbital or translational dynamics.
The approximation of a spacecraft as a point mass rather than an extended rigid body severely limits the applicability and ignores a major component of the dynamic environment.
This work directly derives the equations of motion of a dumbbell spacecraft around an asteroid described using a polyhedron potential model. 
We explicitly consider the impact of the gravitational moment on both the orbit and attitude dynamics. 
With this accurate equations of motion we develop geometric nonlinear controllers which allow for the vehicle to track a desired landing trajectory. 
The landing portion allows for an end to end mission design scheme based on rigorous geometric mechanics techniques.

\bibliographystyle{AAS_publication} 
\bibliography{library}

>>>>

The desired attitude command is chosen such that the spacecraft camera axis, \( \vb{b}_1 \), is directed along the nadir towards the asteroid.
It is sufficient to define two orthogonal vectors to uniquely determine the attitude of the spacecraft.
The \( \vb{b}_{3d} \) vector is chosen to lie in the plane spanned by \(\vb{b}_{1d} \) and \( \vb{e}_3 = \vb{f}_3 \).
The desired attitude command is defined as
\begin{align}
    \vb{b}_{1d} &= - \frac{\vb{x}}{\norm{\vb{x}}} , \\
    \vb{b}_{3d} &= \frac{\vb{f}_3 - \parenth{\vb{f}_3 \cdot \vb{b}_{1d}} \vb{b}_{1d}}{\norm{\vb{f}_3 - \parenth{\vb{f}_3 \cdot \vb{b}_{1d}} \vb{b}_{1d}}}, \\
    \vb{b}_{2d} &= \vb{b}_{3d} \times \vb{1d} , \\
R_d &= \begin{bmatrix} \vb{b}_{1d} & \vb{b}_{2d} & \vb{b}_{3d} \end{bmatrix} .
\end{align}
The camera axis is aligned with the spacecraft \( \vb{b}_ 1 \) axis, which is direted towards the asteroid, throughout the landing trajectory as the spacecraft moves in the equatorial plane of the asteroid.

The simulation is carried out over \SI{7200}{\second} with the spacecraft following a circular trajectory for the first \SI{3600}{\sec} before vertically descending in the body fixed frame for the last \SI{3600}{\second}.
\Cref{fig:true_landing_trajectory} shows a view from the positive \( \vb{f}_3 \) pole of the asteroid of the simulated trajectory. 
The position of the center of mass of the dumbbell is shown in blue, while the pointing direction of the camera view axis is defined in red. 
The attitude of the dumbbell is displayed at several points along the trajectory demonstraiting the pointing of the camera. 
Furthermore, asteroid Itokawa is shown in it's final orientation at the completion of the landing simulation. 
\Cref{fig:pos_components} shows that the nonlinear controller is able to accurately track the desired translational trajectory for the duration of the simulation.
\begin{figure}[htbp]
    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/traj_fig.pdf} 
        \caption{Planar view of landing trajectory\label{fig:true_landing_trajectory}} 
    \end{subfigure}~
    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/pos_fig.pdf} 
        \caption{Position of spacecraft in the inertial frame\label{fig:pos_components}} 
    \end{subfigure} 
    \caption{Landing trajectory to asteroid Itokawa~\label{fig:position}}
\end{figure}

Concurrent with the simulation, we generate images of Itokawa using Blender, as described earlier.
The images are generated at a rate of \SI{1}{\hertz} and stored for post processing and one exampel view is shown in~\cref{fig:example_image}. 
From these images we estimate the position of the camera relative to the asteroid using monocular localization.
In this work, we demonstrate the ability to generate realistic imagery and the processing of these images to determine a state estimate of the camera pose.
In future work, we seek to use this state estimate in a closed-loop controller to enable a fully-autonomous control system for the spacecraft. 
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/test000837.png}
    \caption{Example image of Itokawa at \( t = \SI{837}{\second}\)\label{fig:example_image}}
\end{figure}
From each image, a series of features are detected and tracked between subsequent frames.
A visualization of this process is shown in~c\ref{fig:orbslam_mappoints} which shows the tracked features of the image in green.
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.75\textwidth, keepaspectratio]{figures/orbslam_mappoints.png}
    \caption{ORB-SLAM2 Feature Tracking Visualization\label{fig:orbslam_mappoints}}
\end{figure}
% TODO: Plots of trajectory

% TODO: Control input plot
% TODO: Show estimation from SLAM
\section{Conclusions}\label{sec:conclusions}
There have been a variety of approaches for the analysis and design of orbital trajectories around asteroids.
Relatively less work has been directed towards the design of landing trajectories.
Furthermore, much of the previous work has only treated the orbital or translational dynamics.
The approximation of a spacecraft as a point mass rather than an extended rigid body severely limits the applicability and ignores a major component of the dynamic environment.
This work directly derives the equations of motion of a dumbbell spacecraft around an asteroid described using a polyhedron potential model. 
We explicitly consider the impact of the gravitational moment on both the orbit and attitude dynamics. 
With this accurate equations of motion we develop geometric nonlinear controllers which allow for the vehicle to track a desired landing trajectory. 
The landing portion allows for an end to end mission design scheme based on rigorous geometric mechanics techniques.

\bibliographystyle{AAS_publication} 
% \bibliography{library}
\bibliography{library_local}
